---
title: "p8105_hw1_thb2114"
output: github_document
---
```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(palmerpenguins)
```

# Problem 1
The code chunk below creates a dataframe containing a random sample of size 10 from a standard Normal distribution and constructs a logical vector indicating whether the elements of the sample are greater than 0. It also creates a character vector of length 10 and a factor vector of length 10 with 3 different factor "levels". 

```{r}
problem1_df = tibble(
    sample = rnorm(10),
    gr_than_0 = sample > 0,
    vec_char = c("This","creates","a","character","vector","with","a","length","of","ten"),
    vec_factor = factor(c("low","medium","high","low","medium","high","low","medium","high","low")))
```

I will now try to take the mean of each variable in my dataframe.

```{r, collapse = TRUE}
mean(pull(problem1_df,sample))
mean(pull(problem1_df,gr_than_0))
mean(pull(problem1_df,vec_char))
mean(pull(problem1_df,vec_factor))
```

The character vector and factor variables don't produce means, but the logical variable does. 

I will now apply the 'as.numeric' function to the logical, character, and vector variables.

```{r, eval = FALSE}
as.numeric(pull(problem1_df,gr_than_0))
as.numeric(pull(problem1_df,vec_char))
as.numeric(pull(problem1_df,vec_factor))
```

The 'as.numeric' function turns the logical and factor variables into numeric variables, but it does not do the same for the character variable. This further illustrates why a mean could not be calculated for the character variable. The character variable can not be easily changed into a number, unlike the logical and factor variables.

# Problem 2
The code chunk below will load the 'penguins' dataset from the 'palmerpenguines' package, and will provide information about its contents. 

```{r, eval= FALSE}
data("penguins", package = "palmerpenguins")
penguins
names(penguins)
nrow(penguins)
ncol(penguins)
mean(na.omit(pull(penguins,flipper_length_mm)))
mean(na.omit(pull(penguins,bill_length_mm)))
```

The variable names in this dataset include: `r names(penguins)`. The mean flipper length (mm) of the penguins is `r mean(na.omit(pull(penguins,flipper_length_mm)))` and the mean bill length (mm) is `r mean(na.omit(pull(penguins,bill_length_mm)))`. The dataset includes `r ncol(penguins)` columns and `r nrow(penguins)` rows.

The following code chunk will create a scatter plot with flipper length (mm) on the y-axis and bill length (mm) on the x-axis, and will save it to my project directory.

```{r, collapse = TRUE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```



